Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-21 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Fixes
Update appendix-proofs-for-strongly-separable-examples.tex
Fixed the bad reference (coming from merging the definitions of the two separability notions)

The key observation is that $\Exp[B] = (K-1) \Exp[C]$.
To see this, note that if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
guesses the correct label ($z_t = 0$) and with probability $(K-1)/K$ algorithm's guess is
incorrect ($z_t = 1$). Therefore,
\[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }, \]
\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }. \]

@@

Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
\endgroup
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
then $\widehat y_t \neq y_t$, by
Equation~\eqref{equation:strong-linear-separability-3}, we have that
$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.

>>>>

The key observation is that $\Exp[B] = (K-1) \Exp[C]$.
To see this, note that if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
guesses the correct label ($z_t = 0$) and with probability $(K-1)/K$ algorithm's guess is
incorrect ($z_t = 1$). Therefore,
\[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \indicator{S_t = \emptyset} }, \]
\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \indicator{S_t = \emptyset} }. \]

@@

Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
\endgroup
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:weak-linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
then $\widehat y_t \neq y_t$, by
Equation~\eqref{equation:strong-linear-separability-3}, we have that
$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.
